Thank you, next: demographic consequences of partner diversity and turnover in a multi-species ant-plant mutualism

### 2024-08-19 Manuscript/ant_cactus_AmNat.tex
Update ant_cactus_AmNat.tex

Additional reproductive parameters for the number of seeds per fruit, probability of entry to the seed bank, germination rates, and recruit size were estimated following methods described in Appendix XX.
Estimates for the number of seeds per fruit were ant specific, but the data (cite tom's data) only included \textit{L. apiculatum} and \textit{C. opuntiae} ants.
\tom{We used the vacancy estimates for plants tended by other ants. }{This is an assumption that needs to be explained or justified. Reviewers will ask if results are sensitive to this assumption.}
\tom{The rest of these parameters were not ant specific. }{Because the seed number model is ant-specific, I suggest moving it from the appendix to the main text.}

>>>>

Additional reproductive parameters for the number of seeds per fruit, probability of entry to the seed bank, germination rates, and recruit size were estimated following methods described in Appendix XX.
\tom{Estimates for the number of seeds per fruit were ant specific}{I think this should be expanded. The data come from an experiment where we excluded ants, so this is a real strength (relative to the rest of the observational data) that we should not undersell.}, but the data (cite tom's data) only included \textit{L. apiculatum} and \textit{C. opuntiae} ants.
\tom{We used the vacancy estimates for plants tended by other ants. }{This is an assumption that needs to be explained or justified. Reviewers will ask if results are sensitive to this assumption.}
\tom{The rest of these parameters were not ant specific. }{Because the seed number model is ant-specific, I suggest moving it from the appendix to the main text.}
